\papertitle

### 2014-03-19 final-report/paper.tex
more intro

>>>>

\item A view for communication between workers. A directed link between two fragments in the physical query plan DAG
represents source workers sending tuples to destination workers. Upon clicking on a link, the visualization renders the
worker communication view. This shows the aggregate number of tuples exchanged between workers as well as a time series
charting the number of tuples exchanged over time.
